Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-03-15 PAPER.tex
Commenting a repeat statement.

The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss. This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with the foreground cleaning of Green Bank Telescope (GBT) data. Therefore, in our revised 
signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:crossterm_full}.
weighted power spectrum of the data from the weighted power spectrum of data plus EoR.

>>>>

%The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
%simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss. This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with the foreground cleaning of Green Bank Telescope (GBT) data. Therefore, in our revised 
%signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:crossterm_full}.
%weighted power spectrum of the data from the weighted power spectrum of data plus EoR.
